MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in applications.

>>>>

The goal of all parties involved in the community is to maximize their long-term outcome of their collaboration. Web services need to be utilized with a selection strategy to choose from all the different possible collaboration groups they can form and also an estimation method for evaluating the long-term gain of joining different possible communities. Web services need to experiment different possible collaborative groups with other web services in order to be able to estimate their gain over time. However with high number of possible communities and many other business restrictions its not possible to test run collaboration with random web services. Even if a linear approximate function for estimating utility base on community web services' parameters is adopted, the exponential \footnote{Bell number: $http://en.wikipedia.org/wiki/Bell_number$} growth rate of possible number of partition of web services into communities, would make any brute-force type algorithm for best community selection strategy intractable and non-practical in real-world application settings.
